\input{premath.tex}
%quotes
\newcommand{\citeauthorandyear}[2][]{
   \citeauthor{#2} (\citeyear[#1]{#2})
}
\newcommand{\argmin}{\mathrm{argmin}}
%
\title{DC programming}
\author{Frédéric Boileau}
\date{}
\addbibresource{dcproject.bib} 
\pagestyle{fancy}	
\begin{document}
\maketitle
\tableofcontents
\clearpage

\section{Introduction}
\input{introduction.tex}
\clearpage
\section{Preliminaries}
\input{preliminaries.tex}
\clearpage
\section{Duality and Optimality}
\input{dualityAndOptimality.tex}
\section{DCA}
\input{dca.tex}
\clearpage

%


\appendix
\clearpage
\printbibliography
\clearpage
\section{authors}
Pham dih tao\\
El Bernoussi\\
JB Hiriart-Urruty\\
R. Ellaia\\
JF Tolland (1979 important paper)

\begin{comment}

\clearpage
It could be argued that convex optimization is, to once again use
Boyd's terminology, a technology, and while it is a very useful and
beautiful tool many real life problems are indeed non convex which
prove to be very resistant to traditional techniques. In those cases
there are different approaches :
\begin{itemize}
	\item Convexification where we approximate the problem
		by a convex one and control the erro
	\item Brute force AI type optimization where we find
		heuristics informed by "real-life" knowledge
		of the problem to find solutions which are
		useful and seem quite correct but with no
		optimality guarantee whatsoever
	\item Carefully extend the tools from convex analysis to some
		well defined cases of where non-convexity arises.
\end{itemize}
In this paper I discuss the third case in the specific context of the difference 
of two convex functions. I assume knowledge of the basics of convex analysis such
as Fenchel duality, lower-semicontinuityo, sub-differentials, epigraphs and relative
interiors. I hope however that the treatment will illuminate and motivate some
of those motivations.  I will start by defining some notation which will be
used throughout the text.  \\The standard DC  Program is the following:
\begin{equation}
	P \qquad \lambda :=	\inf\{g(x) - h(x) \, | \, x\in \mathbb{R}^n\}
	\qquad
	g,h \in \Gamma_0
\end{equation}
At first read this program might seem quite arbitrary and simple. Of all the
ways to start exploring the non-convex realm why choose this one. It turns out
that there are three very good reasons to explore such a program. First and
foremost it is actually a very natural generalization and step outside of
convexity for reasons I will explore later. Moreover there are many real-life
problems which can be very easily modelled by such programs and finally a
powerful algorithm has been developped for DC programs (DCA algorithm) which
although it doesn't guarantee global optimality \emph{does} often converge to
global solutions and does so very robustly and efficiently. Those three factors
suggest the relevance of investigating those programs.  
\end{comment}

\section*{Fairness and efficiency in ressource allocation}
The setting is an optimization problem where we have some
ressources, denoted $i\in R$ and some agents, denoted $j\in J$.
The set of possible allocations $X$ lives in $\mathbb R^{m\times n}$.
Each agent $j$ derives some utility from acquiring some ressource, 
independently of what the others receive.
Say \begin{equation} U_j: \mathbb R^{m} \longrightarrow \mathbb R
\qquad (x_{j1},\ldots,x_{jm})\mapsto u_j\end{equation}
Most classical treatments of ressource allocation in economics focus on
efficiency, that is maximizing utility with little regard to "fairness"
considerations however in some fields the latter is critical.  For example
consider bandwith allocation to different links in a network where each
customer's service depend on different links. Maximizing overall bandwith
might result in some user being completely cutoff which is clearly
unacceptable. Different metrics of fairness have been proposed such as the
Gini and Atkinson indices and there is an associated set of
of properties and a well established axiomatic treatment of notions
of fairness in the litterature.
Moreover there is a tradeoff to be made between fairness and efficiency.
The overall objective function that can model both and prescribe
how one should dominate over the other is called a social welfare functionn.

I'd like to investigate the properties of the problem of optimizing a social
welfare function given a set of constraints and utility functions. More
specifically how the type of utility function and the similarity between them
for different individuals affects the structure of the problem under
classical considerations : convexity and smoothness. Moreover how 
do different choices of social welfare functions affect efficiency and 
fairness.

This is a setting extracted from a case a friend of mine was confronted with 
in the context of his financial consulting work.
When shareholders give some intentions to sell some of their stocks and
there is a maximal number of shares to sell, how does one distribute selling
options across the population in the fairest way. Increased complexity
is injected by the fact that there are different types of shares (e.g.
premium, normal) and agents hold those in different proportions.

Finally in computer heterogeneous  ressource allocation such as cloud computing,
the constraint and utility functions can be dynamic, parametrized by some 
$t\in \mathbb R_+$.


\begin{gather}
    y'' = (x-x^3/(3!) + O(x^5))(y(0) + y'(0)x+ O(x^2)) + cos(x)\\
y'' = xy(0) + y'(0)x^2 - y(0)x^3/(3!) - y'(0)x^4/(4!) + O(x^2)(x-x^3/(3!)) + O(x^5) + cos(x)
\end{gather}
    
\end{document}

